Placing the spotted T Tauri star LkCa 4 on an HR diagram

### 2016-09-13 document/PKU_document/ms.tex
modify the latex file for the PKU postdoc report formatting

%\documentclass[iop,revtex4]{emulateapj}% change onecolumn to iop for fancy, iop to twocolumn for manuscript
\documentclass[twocolumn]{emulateapj}% change onecolumn to iop for fancy, iop to onecolumn for manuscript
%\documentclass[12pt,preprint]{aastex}

%\usepackage{lineno}
%\usepackage{blindtext}
%\linenumbers

\let\pwiflocal=\iffalse \let\pwifjournal=\iffalse
%From: http://arxiv.org/format/1512.00483
%\input{setup}
\input{mgs_setup}

@@

\slugcomment{In preparation}

\shorttitle{Starspots on LkCa 4}

\shortauthors{Gully-Santiago et al.}

\bibliographystyle{yahapj}

@@

\author{Michael A. Gully-Santiago,\altaffilmark{1} Gregory J. Herczeg,\altaffilmark{1} Ian Czekala,\altaffilmark{2}, Garrett Somers\altaffilmark{2}, et al.}

\altaffiltext{1}{Kavli Institute for Astronomy and Astrophysics, Beijing, China}
\altaffiltext{2}{TBD}

@@

\keywords{stars: fundamental parameters --- stars: individual (LkCa 4) ---  stars: low-mass -- stars: statistics}

@@

Table \ref{tbl_order_results} lists all the IGRINS spectral order results.
\LongTables
\input{tables/tbl_order_results.tex}

@@

\acknowledgements
The authors thank Gregory N. Mace for carrying out the IGRINS observations.

MG-S and GJH are supported by general grant 11473005 awarded by the National Science Foundation of China.   The ESPaDOnS observations are supported by the contribution to the MATYSSE Large Project on CFHT obtained through the Telescope Access Program (TAP), which has been funded by the ``the Strategic Priority Research Program---The Emergence of Cosmological Structures'' of the Chinese Academy of Sciences (Grant No.11 XDB09000000) and the Special Fund for Astronomy from the Ministry of Finance.

This work used the Immersion Grating Infrared Spectrograph (IGRINS) that was developed under a collaboration between the University of Texas at Austin and the Korea Astronomy and Space Science Institute (KASI) with the financial support of the US National Science Foundation under grant ASTR1229522, of the University of Texas at Austin, and of the Korean GMT Project of KASI.

This research has made use of NASA's Astrophysics Data System.  The research is based on data from the OMC Archive at CAB (INTA-CSIC), pre-processed by ISDC.
We acknowledge with thanks the variable star observations from the AAVSO International Database contributed by observers worldwide and used in this research.
This publication makes use of data products from the Two Micron All Sky Survey, which is a joint project of the University of Massachusetts and the Infrared Processing and Analysis Center/California Institute of Technology, funded by the National Aeronautics and Space Administration and the National Science Foundation.

{\it Facilities:} \facility{Smith (IGRINS)}, \facility{AAVSO}, \facility{CFHT (ESPaDOnS)}, \facility{INTEGRAL (OMC)}, \facility{ASAS}, \facility{CrAO:1.25m}, \facility{ARC (TripleSpec)}, \facility{Hale (DBSP)}

{\it Software: } 
 \project{pandas} \citep{mckinney10},
 \project{emcee} \citep{foreman13},
 \project{matplotlib} \citep{hunter07},
 \project{numpy} \citep{vanderwalt11},
 \project{scipy} \citep{jones01},
 \project{ipython} \citep{perez07},
 \project{gatspy} \citep{JakeVanderplas2015},
 \project{starfish} \citep{czekala15},
 \project{seaborn} \citep{waskom14}
%\software{%
% \project{pandas} \citep{mckinney10}
%    \project{emcee} \citep{foreman13},
% \project{matplotlib} \citep{hunter07},
% \project{numpy} \citep{vanderwalt11},
% \project{scipy} \citep{jones01},
% \project{ipython} \citep{perez07},
% \project{gatspy} \citep{JakeVanderplas2015},
% \project{starfish} \citep{czekala15}}.

@@

\bibliographystyle{apj}
\bibliography{ms}

>>>>

\documentclass[12pt]{report}
%\documentclass[dvipdfmx]{PostDocRep}

\let\pwiflocal=\iffalse \let\pwifjournal=\iffalse
%From: http://arxiv.org/format/1512.00483
%\input{setup}
\usepackage{amsmath,amsfonts,amsthm,amscd}
\usepackage{amssymb}

\usepackage{stylefiles/aastex_hack}
\usepackage{stylefiles/deluxetable} 
\usepackage{longtable}

\usepackage[numbers]{natbib}
\usepackage[nottoc]{tocbibind}
\usepackage{makeidx}       	% Package to make an index.

\input{mgs_setup}

@@

%\shorttitle{Starspots on LkCa 4}

%\bibliographystyle{yahapj}

@@

\author{Michael A. Gully-Santiago}

@@

%\keywords{stars: fundamental parameters --- stars: individual (LkCa 4) ---  stars: low-mass -- stars: statistics}

\tableofcontents
% ±í¸ñÄ¿Â¼
\listoftables
% ²åÍ¼Ä¿Â¼
\listoffigures

@@

Table \ref{tbl_order_results} lists all the IGRINS spectral order results.
\input{tables/tbl_order_results.tex}

@@

@@

%\bibliographystyle{plainnat}
\bibliographystyle{apj}
\bibliography{ms}
